
% Motivation
LAMMPS fixes are powerful, but sometimes insufficient. Although
modifying LAMMPS' source code allows efficient implementation of
arbitrary fixes, it requires a technical background and
\texttt{C++} to be the language used. Especially when working
with heavyweight or language-specific systems, it would be far
easier to write fixes externally. Thus, we have developed a
system for external force fixes as functions of the entire
simulated system. Furthermore, in cases where such
inter-process communication heavy computation would be overkill,
we provide a custom externally-determined forcing field.

% Bird's eye view
If we want to have an external system act as a ``controller''
over our LAMMPS particles, we will need to define a
\texttt{C++ fix} class which can then be applied in scripts.
Instances of this class will need to be able to communicate
externally: The easiest way to do this is via the Message
Passing Interface (MPI), which LAMMPS already uses. These
``workers'' will send MPI packets to the controller whenever
they need an update, then receiving a result and applying it.
For readability and encoding-independence, we will send packets
using JavaScript Object Notation (JSON). To avoid gridlock, we
will allow the user to specify a maximal time to await
controller response before an error is thrown.

We will call this fix type \textbf{\texttt{fix arbfn}} (for
``arbitrary function'' of the state of the simulation).

Note: JSON incurs overhead cost proportional to the size of the
message because of its syntax. It would be faster and smaller to
send raw encodings of the values used, at the cost of imposing
additional restrictions upon the controller language. Thus, we
have chosen to pay the overhead for JSON.

In the aforementioned special cases wherein constant MPI
communication is unnecessary, we will also define the
\textbf{\texttt{arbfn/ffield}} fix, which determines a static
force field via MPI communication at instantiation, then
trilinearly interpolating atom positions onto a finite grid in
order to find their forcing values at runtime.

% Final LAMMPS interface
Our final \texttt{LAMMPS} interface for \texttt{fix arbfn} is
exemplified by the following.

\lstset{language=bash}
\begin{code}
# Every timestep, send all atomic data and
# receive fix data.  If the controller
# takes longer than 50 ms to respond, error.
fix name_1 all arbfn maxdelay 50.0

# Every 100 timesteps, send all atomic data
# without expecting any fix data back.
fix name_2 all arbfn every 100 dumponly
\end{code}

Likewise, \texttt{fix arbfn/ffield} is shown below.
\begin{code}
# At initialization, retrieve a mesh of 101
# by 201 by 301 nodes. Every timestep,
# perform trilinear interpolation of the
# received force field.
fix name_3 all arbfn/ffield 100 200 300
\end{code}

More about the implementation of these fixes will be given in
section \ref{body}.
